\sysfull

### 2018-04-16 paper/intro.tex
intro is revised

This paper introduces a new system called \sys, which executes a task-based
intermittent program by dynamically coalescing/splitting its tasks.
\sys accepts any static decomposition (i.e., from the programmer or from a compiler) 
and coalesces/splits its tasks at runtime. Two consecutive, coalesced tasks execute  
with no commit or task transition overhead between them, instead performing
task-end commit actions at the end of the second task only.
%
When there is sufficient energy to execute both tasks, two distinct, small
tasks are effectively executed as a single large task, preserving the atomicity
of both. If power fails during a coalesced task, execution restarts from the
{\em first} of the coalesced tasks. Figure~\ref{fig:coalesce} (top)
illustrates how dynamic coalescing changes the earlier execution and highlights
the change in memory model necessary to not break atomicity. On the other hand, a large task that requires more energy to complete than a device's fixed energy buffer is split by \sys to enable task termination, as depicted in Figure~\ref{fig:coalesce} (bottom).

>>>>

This paper introduces a new system called \sys, which executes a task-based
intermittent program by dynamically coalescing/splitting its tasks.
\sys accepts any static decomposition (i.e., from the programmer or from a compiler) 
and coalesces/splits its tasks at runtime. Two consecutive, coalesced tasks execute  
with no commit overhead between them, instead performing
task-end commit actions at the end of the second task only.
%
When there is sufficient energy to execute both tasks, two distinct, small
tasks are effectively executed as a single large task, preserving the atomicity
of both. If power fails during a coalesced task, execution restarts from the
{\em first} of the coalesced tasks. Figure~\ref{fig:coalesce} (top)
illustrates how dynamic coalescing removes unnecessary overhead and shortens intermittent program execution. 
On the other hand, a large task that requires more energy to complete than a device buffered energy 
is split by \sys to enable task termination and preserve execution progress, as depicted in Figure~\ref{fig:coalesce} (bottom).
